Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-24 lineages_18Q3.Rmd
updated rmd

```{r}
crispr_data <- readRDS("./data_munging/rds/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
```

@@

@@

```{r}
crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_lineage.rds")
```

>>>>

```{r}
crispr_data <- readRDS("./data_munging/rds/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
# write.table(crispr_data, file = "crispr_data.tsv", quote = FALSE, sep = "\t")
```

```{r, include=FALSE, eval=FALSE}
length(intersect(unique(crispr_data$Hugo_Symbol), unique(maf_df$Hugo_Symbol)))
length(intersect(unique(crispr_data$Hugo_Symbol), unique(cn_melt$Hugo_Symbol)))
length(intersect(unique(crispr_data$Hugo_Symbol), unique(ge_melt$Hugo_Symbol)))

length(intersect(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID)))
length(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)))
length(intersect(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID)))

length(intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
setdiff(crispr_data$Broad_ID, intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
```

@@

# Mutation exploration

```{r}
maf_annot <- merge(maf_raw[maf_raw$Variant_Classification != "Silent",] %>% group_by(Broad_ID) %>% tally(), crispr_meta, by = "Broad_ID", all.y = TRUE)
```

```{r fig.height=6, fig.width=12}
ggplot(data = maf_annot, aes(x = primary_tissue, y = n)) +
  geom_jitter(alpha = 0.6, size = 0.7, position = position_jitter(w = 0.15)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

```{r}
crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_lineage.rds")

knitr::kable(filter(crispr_signif_lineage, p < 0.1)[, c(1, 2, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```
